The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-07 Writeup/paper_v3.tex
another addressed comment

There is one subtlety in our method used for estimating
completeness. We have used the full $m_\text{F814W}\le23.5$ sample
for identifying
overdensities and for the completeness calculations that motivated our
definitions of volume-limited samples. (\rachel{Do the numbers in the
  table include the full sample or just the subsample with postage stamps?} \arun{The subsample alone. The only place where the full sample is used is Fig. 3. The following sentence is corrected to say that.}) However, everywhere else in the paper, we consider only those galaxies for which there are postage stamp
images used to create weak lensing simulations, in part because this is the
sample for which fits to \sersic\ profiles were carried out, which is a
requirement for our morphology analysis.  
12 per cent of the galaxies that pass our cuts do not have an
associated postage stamp image.
Postage stamps may not exist because, given the size of the galaxy,
the size of the postage stamp we want to draw around it (including
some blank space) intersects the edge of the CCD.
If all galaxies were the same size, this would be a purely random effect, but in fact bigger galaxies are more likely to get excluded by this cut. 
It is commonly the case that  galaxies that are nearby and
intrinsically very bright do not have postage stamps associated with
them, an effect that is dominant at lower redshifts (and is part of
our reason for excluding $z<0.3$). 
Our completeness calculation is done at high redshifts, and thus we
believe that our conclusions are not affected by this bias.

>>>>

There is one subtlety in our method used for estimating
completeness. We have used the full $m_\text{F814W}\le23.5$ sample
for identifying
overdensities and for the completeness calculations that motivated our
definitions of volume-limited samples.  However, everywhere else in the paper, we consider only those galaxies for which there are postage stamp
images used to create weak lensing simulations, in part because this is the
sample for which fits to \sersic\ profiles were carried out, which is a
requirement for our morphology analysis.  
12 per cent of the galaxies that pass our cuts do not have an
associated postage stamp image.
Postage stamps may not exist because, given the size of the galaxy,
the size of the postage stamp we want to draw around it (including
some blank space) intersects the edge of the CCD.
If all galaxies were the same size, this would be a purely random effect, but in fact bigger galaxies are more likely to get excluded by this cut. 
It is commonly the case that  galaxies that are nearby and
intrinsically very bright do not have postage stamps associated with
them, an effect that is dominant at lower redshifts (and is part of
our reason for excluding $z<0.3$). 
Our completeness calculation is done at high redshifts, and thus we
believe that our conclusions are not affected by this bias.
